Unsupervised embedding of trajectories captures the latent structure of mobility

### 2021-04-15 paper/current/main.tex
switch to science citation style
reflect yy comment

% Refs
%\usepackage{scicite}
\usepackage[style=nature,
					backend=biber,
					sortcites=true,
					autocite=superscript
]{biblatex}

@@

%
% ABSTRACT
%
\newpage
\begin{sciabstract}
	Human mobility drives major societal phenomena including epidemics, economies, and innovation.
	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
	We propose using the neural embedding model \textit{word2vec} for studying mobility and capturing its complexity.
    \textit{Word2ec} is shown to be mathematically equivalent to the gravity model of mobility, and using using three human trajectory datasets, we demonstrate that it encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance that outperforms baselines.
	Focusing on the case of scientific mobility, we show that embeddings uncover cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
	Connecting neural embeddings to the gravity model opens up new avenues for the study of mobility.
\end{sciabstract}

>>>>

% Refs
%\usepackage{scicite}
\usepackage[style=science,
					backend=biber,
					sortcites=true,
					autocite=superscript
]{biblatex}

@@

%
% ABSTRACT
%
\newpage
\begin{sciabstract}
	Human mobility drives major societal phenomena including epidemics, economies, and innovation.
	Historically, mobility was constrained by geographic distance, however, in the globalizing world, language, culture, and history are increasingly important.
	Here, we show the mathematical equivalence between \textit{word2vec} model and the gravity model of mobility and the demonstrate that, by using three human trajectory datasets, \textit{word2vec} encodes nuanced relationships between locations into a vector-space, providing a measure of effective distance.
	Focusing on the case of scientific mobility, we show that embeddings uncover cultural, linguistic, and hierarchical relationships at multiple levels of granularity.
	Connecting neural embeddings to the gravity model opens up new avenues for the study of mobility.
\end{sciabstract}
